The Sloan Digital Sky Survey Spectroscopic Reduction Pipeline

### 2006-03-29 doc/paper/paper2d.tex
Added spectrograph info

%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
\section{OPTIMAL EXTRACTION}
\label{sec_extract}

>>>>

%------------------------------------------------------------------------------
%------------------------------------------------------------------------------
\section{SDSS SPECTROGRAPHS}
\label{sec_spectrographs}

The SDSS spectroscopic survey was carried out with twin multi-fiber 
spectrographs mounted at the back of the SDSS telescope (see Gunn et al.
2006).  One of nine spectrograph cartidges can be mounted for a single
spectroscopic observing sequence.  The cartridge holds a single aluminum
plate, 813mm in diameter, pre-drilled and plugged with 640 fibers 
fed into the twin spectrographs, 
and 11 coherent fibers fed into a simple air-cooled camera (model \#??)
for telescope guiding.

The fibers are 180 $\mu m$ in diameter and subtend 2.97" at Cassegrain focus.
The fibers accept the f/5 beam directly and, due to focal degradation, input
an f/4 exit beam into each of the spectrographs.  The fibers are mounted in
bundles of 20 with inter-fiber spacings of 390 $\mu m$.  Sixteen bundles are
mounted on a single slithead with a radius of curvature of 640 mm and have
an extra spacing of approximately 200 $\mu m$ between bundles.

In Figure 1, we show a top-view schematic of one the spectrographs, and
will detail the light path below starting at the slithead.
The output light from the fiber is collimated with a spherical mirror
(radius of curvature is 1264 mm), which is aligned by 3 motor mounts to
control focus, tip \& tilt.  A left/right hartmann mask 
covers the collimator to act as both a spectrograph shutter and traditional 
shack-hartmann mask for focus tests.  The collimator in spectrograph 2
was coated with an enhanced silver coating and delivers slightly higher
reflectivity compared to the aluminum coated collimator in spectrograph 1.
The collimated beam encounters a 40mm thick dichroic (beamsplitter) which
reflect light blueward of 6000$\AA$.  The blue reflected light is dispersed
with a 640 l/mm grism with zero deviation at 4960$\AA$.  The red transmitted
light is dispersed with a 440 l/mm grism with zero deviation at 7400$\AA$.
The dispersed light in each arm of the spectrograph enters a transmission camera
wth a 240mm focal length (demagnification of 2.5) which is tuned for the 
corresponding range of wavelengths.  Each of the 4 camera produce RMS 
spot sizes of approximately 20$\mu m$ over a 16.5$\degree$ diameter 
f.o.v. delivered to a single thinned Tektronix 2048x2048x24$\mu m$ CCD.
An external focus ring is adjustable by hand for each CCD camera to accomodate
differential focus changes not corrected with the common collimator.
The four spectrograph cameras are labeled "b1, r1, b2, r2".

\section{OPTIMAL EXTRACTION}
\label{sec_extract}
